ZCB Pricing

### 2018-08-02 ZCB Pricing .Rmd
Convergence test for rates

  Diag_1 <- matrix(0,ncol = M, nrow = M)
    # Main diagonal of matrix

  for (j in 1:M){
    Diag_1[j,j] <- pm(j)

@@

  dt <- T/N # Length of each time subinterval
  dr <- J[2] -J[1] # Lenght of each rate subinterval
  #===========================================================================================
  # Define the following functions for j = 1,...,M at each time point i

@@

  pu <- function(j){
    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2))

  #===========================================================================================
  # Define 2 tridiagonal matricies. One for time point i and one for time point i+1

@@

  # Main diagonal of matrix 1
  for (j in 1:M){
    Diag_1[j,j] <- -1/dt - pm(j)

@@

  # Main diagonal of matrix 2
  for (j in 1:M){
    Diag_2[j,j] <- -1/dt + pm(j)
    }

@@

  #===========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0

@@

```{r}
# Covergence tests for Monte Carlo functions

>>>>

  Diag_1 <- matrix(0,ncol = M, nrow = M)

  # Filling main diagonal of matrix 
  for (j in 1:M){
    Diag_1[j,j] <- pm(j)

@@

  dt <- T/N # Length of each time subinterval
  dr <- J[2] -J[1] # Lenght of each rate subinterval

  #========================================================================================
  # Define the following functions for j = 1,...,M at each time point i

@@

  pu <- function(j){
    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2)) 
  }

  #========================================================================================
  # Define 2 tridiagonal matricies. One for time point i and one for time point i+1

@@

  # Filling main diagonal of matrix 1
  for (j in 1:M){
    Diag_1[j,j] <- -1/dt - pm(j)
  }

@@

  # Filling main diagonal of matrix 2
  for (j in 1:M){
    Diag_2[j,j] <- -1/dt + pm(j)
    }

@@

  #========================================================================================
  # Constructing more matricies and iterating the procedure from maturity to time 0

@@

```{r 14}
# Convergence Tests for finite difference methods
# Varying rate steps

# rate_step <- c(0.02,0.016,0.012,0.010,0.008,0.006,0.005,0.004,0.003,0.002)
# rate_vec <- NULL
# for (i in 1:length(rate_step)){
#   rate_vec[i] <- length(seq(-0.4,0.6,rate_step[i])) 
# }
# 
# 
# closed_r <- NULL
# CN_conv_1 <- NULL
# Impl_conv_1 <- NULL
# Expl_conv_1 <- NULL
# 
# 
# 
# for (i in 1:length(rate_step)){
#   closed_r[i] <- bond_price()
# }
# 
# for (i in 1:length(rate_step)){
#   CN_conv_1[i] <- CN(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# for (i in 1:length(rate_step)){
#   Impl_conv_1[i] <- implicit(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# for (i in 1:length(rate_step)){
#   Expl_conv_1[i] <- explicit(J = seq(-0.4,0.6,rate_step[i]))
# }
# 
# par(mfrow = c(1,1))
# plot(closed_r, x = rate_vec, type = "l", xlab = "Number of time steps", ylab = "Estimated Price")
# lines(x = rate_vec, y = CN_conv_1, type = "l", lty = 2)
# lines(x = rate_vec, y = Impl_conv_1, type = "l", lty = 3, col = "blue")
# lines(x = rate_vec, y = Expl_conv_1, type = "l", lty = 4, col = "red")
# legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)

```{r 15}
# Covergence tests for Monte Carlo functions
